NinasTech is a company to connect and support  girls 
who are studying in areas related to technology.

Mission: Help and influence girls to work in the technology field.

Vision: Be a connection between  girls, helping with a group study and free information for job opportunities.

Values:  Volunteering, Union, Diversity, Freedom.

mental-health
ninastech-team
work-with-us
web developer
ninas-talk
english-speakers
connect-&-study

Ninastech is a unique company that provides theoretical and practical programming knowledge. 
In addition  we also offer psychological support for working with technology.
It is not enough to have knowledge or ability to learn programming, you need resilience, perseverance and believing in yourself.


We work as a team of mentor volunteers that can help you until you are confident to get the job!


Networking
 
Find developers to collaborate with and make new friends from other countries. 
Volunteering  gives you the opportunity to learn more about the field, about the tasks of that position, before jumping headlong into a company with more intense demands.

Be different

Companies are looking for professionals who know how to work in a team,  who know how to manage their time. As you progress in your career with these experiences, you will be able to tell the stories of these learnings in interviews and also use these skills in industry positions. 

Skills & Experience 

Volunteering will provide you with a space to learn, make mistakes, improve and grow. Is a very rich opportunity  to learn new skills, improve existing skills and also teach others around you.  

Web developer 
HTML
CSS
JavaScript
Design with Figma
Node.js 


Almost ever Sunday we have meetings with students or peolple that work in tech. They inspire us with informations and storys about careers .

English Speakers
Free nice conversations in English
Training for interviews
Read english books together  
